---
title: "Heart disease dataset"
output: html_document
date: "2024-05-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("utils.R")

plots.dir <- "../plots/"
```


## Dataset

```{r}
heart <- read.csv("../data/heart.csv")

target <- 14
dataset.distrib(heart[,target])
```

- age
- sex
- chest pain type (4 values)
- resting blood pressure
- serum cholestoral in mg/dl
- fasting blood sugar > 120 mg/dl (true or false)
- resting electrocardiographic results (values 0,1,2)
- maximum heart rate achieved
- exercise induced angina (yes or no)
- oldpeak = ST depression induced by exercise relative to rest
- the slope of the peak exercise ST segment
- number of major vessels (0-3) colored by flourosopy
- thal: 0 = normal; 1 = fixed defect; 2 = reversable defect

```{r}
boxplot(scale(heart[,-target]))

summary(heart[,-target])
```

```{r}

```


## Logistic regression

```{r}
library(glmnet)
```

```{r}
logist <- glm(target ~ ., data=heart, family="binomial")

summary(logist)
first.metrics(2 * heart$target - 1, ifelse(logist$fitted.values > 0.5, 1, -1))
```

```{r}
logist.reg <- glmnet(as.matrix(heart[,-target]), heart[,target], family="binomial", alpha=0)
```

```{r}
plot(logist.reg, xvar="lambda")
legend("bottomright", legend=colnames(heart[,-target]), cex=0.8)
```


## Cluster analysis

Find subgroups in variables

```{r}

```

